Comparing tool variability and numerical variability in fMRI analyses

### 2021-10-25 paper/paper.tex
minor changes

It is notable that we obtained more uncertainty on thresholded results than unthresholded maps, %This issue is 
probably due to different thresholding values used in different tools.
This is consistent with the observations in~\cite{bowring2021isolating} where identified a high correlation between unthresholded t-statistic maps,
but substantially low Dice coefficient for activations in the thresholded maps.
This raises further investigations on thresholding techniques to reduce instabilities.

Given that FL only perturbs basic mathematical functions, we expect more numerical variability by perturbing linear algebra,
in particular for non-scalar types like vectors or matrices. For the future study, this can be evaluated using MCA-instrumented versions 
of BLAS and LABACK along with other libraries available in the Fuzzy project in Verificarlo's GitHub repository at github.com/verificarlo/fuzzy.

@@

\begin{itemize}

    \item[$\bullet$ ] Further studies can be evaluating the numerical stabilities within tool by focusing on the particular parts of
    the pipeline that has been identified as the main sources of variations in~\cite{bowring2021isolating}.
    Also, we can invetigate the precision in WT variability that simulates mostly BT variability in the furure study.

\end{itemize}

\section{Acknowledgments}

>>>>

It is notable that we obtained more uncertainty on thresholded results than unthresholded maps, %This issue is 
probably due to different thresholding values used in different tools.
This is consistent with the observations in~\cite{bowring2021isolating} where identified a high correlation between unthresholded t-statistic maps,
but substantially low Dice coefficient for activations in the thresholded maps.
This raises further investigations on thresholding techniques to reduce the associated instabilities.

Given that FL only perturbs basic mathematical functions, we expect more numerical variability by perturbing linear algebra,
in particular for non-scalar types like vectors or matrices. For the future study, this can be evaluated using MCA-instrumented versions
of BLAS and LAPACK along with other libraries available in the Fuzzy project in Verificarlo's GitHub repository at github.com/verificarlo/fuzzy.

@@

We presented a comparison study between numerical variability introduced by floating-point perturbations and tool variability arised from software package variations.
For an fMRI analysis, we measured a significant variability in both conditions, which was comparable for some brain regions.
We showed the FL library as a valuable model based on MCA method for simulating the numerical variability.
Moreover, we can leverage the MCA-instrumented libraries for simulating the numerical uncertainty in different studies.

Further work can be done to evaluate and localize the numerical stabilities within tools by focusing on the particular parts of
the pipeline that has been identified as the main sources of variations in~\cite{bowring2021isolating}.
This helps to identify the accurate source of instabilities within pipelines and gradually improve the stability of the pipeline components.
